Response to reviewers

### 2022-02-16 response/response1.Rmd

* **Need help** XXX We need to review this literature. It's not true that we have ignored it, the main reference is Dasu! But we need to decide whether there is more that we should cite.

>>>>

We agree that there is substantial literature on data cleaning. We have referenced one of the main works, Dasu and Johnson (2003) but don't feel it is necessary to cite more than this. We have similarly only pointed to one main reference for IDA and EDA.
